DOM Review: Initial analysis

### 2023-02-09 Analysis/Code/2_InitialAnalysis.Rmd

  ggplot() +
  geom_boxplot(aes(x = `Study Size`, y = NumSites), colour = "darkred") +
  scale_y_continuous(trans = "log10") + 
  labs(title = "Number of sites by study size",
       x = "Study size (km2)", y = "Number of Sites (log transformed)") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) 
```
### Covariates by site count

@@

```{r Parameter table, echo = FALSE}
covData %>% 
  group_by(`Review ID`, Parameter) %>% 
  summarise() %>%
  group_by(Parameter) %>%
  summarise(`Number of papers` = n()) %>%
  arrange(-`Number of papers`) %>% 
  mutate(Percentage = `Number of papers` / 54)
  kable()
```

### Multi-species
*9* models included at least one multi-species parameter.
```{r Multi-species papers, echo = FALSE}
covData %>%
  group_by(`Review ID`, MultiSpecies, Parameter) %>%
  summarise() %>%
  group_by(`Review ID`) %>%
  summarise(MultiSpecies = sum(MultiSpecies)) %>%
  mutate(MultiSpecies = case_when(MultiSpecies >0 ~ 1,
                                  MultiSpecies == 0 ~ 0)) %>%
  summarise(sum(MultiSpecies))
```

@@

### Selection method
The majority of papers selected models **a priori** (either single or multiple)
```{r Selection category, echo = FALSE}
modelData %>%
  group_by(`Review ID`, Select_Category) %>%
  summarise() %>%
  group_by('Selection category' = Select_Category) %>%
  summarise(Percent = n()/54) %>%
  arrange(-Percent) %>%
  kable()
```

>>>>

  ggplot() +
  geom_boxplot(aes(x = `Study Size`, y = NumSites), colour = "darkred") +
  scale_y_continuous(trans = "log10") + 
  labs(title = "Number of sites by study size",
       x = "Study size (km2)", y = "Number of Sites (log transformed)") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) 
```

### Covariates by site count

@@

```{r Parameter table, echo = FALSE}
covData %>% 
  group_by(`Review ID`, Parameter) %>% 
  summarise() %>%
  group_by(Parameter) %>%
  summarise(`Number of papers` = n()) %>%
  arrange(-`Number of papers`) %>% 
  mutate(Percentage = `Number of papers` / 54) %>%
  kable()
```

### Multi-species
*9* models included at least one multi-species parameter.
```{r Multi-species papers, echo = FALSE, include = FALSE}
covData %>%
  group_by(`Review ID`, MultiSpecies, Parameter) %>%
  summarise() %>%
  group_by(`Review ID`) %>%
  summarise(MultiSpecies = sum(MultiSpecies)) %>%
  mutate(MultiSpecies = case_when(MultiSpecies >0 ~ 1,
                                  MultiSpecies == 0 ~ 0)) %>%
  summarise(sum(MultiSpecies))
```

@@

### Selection method
The majority of papers selected models **a priori** (either single or multiple)
```{r Selection category, echo = FALSE}
modelData %>%
  group_by(`Review ID`, Select_Category) %>%
  summarise() %>%
  group_by('Selection category' = Select_Category) %>%
  summarise(Percent = n()/54) %>%
  arrange(-Percent) %>%
  kable(digits = 2)
```
